---
title: "Ejercicios de Based Stock Policy"
output: html_notebook
---
 
## Ejercicio clase  
Tenemos un sandwich que nos cuesta producir $10/unidad.  
Nos cuesta producirlo $6/unidad  
El precio de salvamento es de: $4/unidad  

Tenemos un costo de transporte de $0.5 (que tiene que pagar el productor)  

```{r}
cu=10-6 #sobrantes
paste("El costo de los sobrantes es de:  ", cu)
co=6-4+0.5 #faltantes
A<-rbind(c(1,2,3),c(2,2,2))
print("La matriz A:")
print(A)

ratio<-cu/(co+cu) #critical ratio
 paste("El critical ratio es de:  ", ratio)
```

## Lecturas relvantes:  
https://medium.com/analytics-vidhya/newsvendor-inventory-problem-with-r-ccfc5a505f38  
http://www.stat.umn.edu/geyer/old/5101/rlook.html   


## Ejercicio 2

```{r}
sellingPrice = 10#$/unit
salvage = 2
productionCost = 3.5#$/unit

co = productionCost - salvage
cu = sellingPrice - productionCost
criticalRatio<-cu/(cu+co)

demand <- c(250,300,350,400,450,500) # pizza
probabilities <- c(0.25,0.20,0.20,0.15,0.1,0.1) # pizza
probabilitiesC<-cumsum(probabilities)

#Para 350
Q = 350
NumOver <- ifelse(Q - demand >= 0, (Q - demand)*probabilities, 0)
NumUnder <- ifelse(demand - Q >= 0, (demand - Q)*probabilities, 0)
CostOver <- co*NumOver
CostUnder <- cu*NumUnder
TotalCost <- CostOver+CostUnder


sumCostOver<-ceiling(sum(CostOver))
sumCostUnder<-ceiling(sum(CostUnder))
totCost<-ceiling(sum(TotalCost))

#Pregunta 2
probabilitiesC<-cumsum(probabilities)

aprox<-which(abs(probabilitiesC - criticalRatio) == min(abs(probabilitiesC - criticalRatio)))
optQ<-demand[aprox]

#Pregunta 3
Q2 = 400
NumOver2 <- ifelse(Q2 - demand >= 0, (Q2 - demand)*probabilities, 0)
NumUnder2 <- ifelse(demand - Q2 >= 0, (demand - Q2)*probabilities, 0)
CostOver2 <- co*NumOver2
CostUnder2 <- cu*NumUnder2
TotalCost2 <- CostOver2+CostUnder2


sumCostOver2<-ceiling(sum(CostOver2))
sumCostUnder2<-ceiling(sum(CostUnder2))
totCost2<-ceiling(sum(TotalCost2))


Q3 = 450
NumOver3 <- ifelse(Q3 - demand >= 0, (Q3 - demand)*probabilities, 0)
NumUnder3<- ifelse(demand - Q3 >= 0, (demand - Q3)*probabilities, 0)
CostOver3 <- co*NumOver3
CostUnder3 <- cu*NumUnder3
TotalCost3 <- CostOver3+CostUnder3


sumCostOver3<-ceiling(sum(CostOver3))
sumCostUnder3<-ceiling(sum(CostUnder3))
totCost3<-ceiling(sum(TotalCost3))

```




## Ejercicio 4
The Litengine Company manufactures piston engines for ultra-light aircraft. The company considers making a last production run of an old-model engine that is going to be eliminated within a year.  

The unit production cost is \$1000, and the engine sells for \$1800. Engines not sold will be moved to a faraway junkyard, at a transportation and handling cost of \$180 per unit. The junkyard pays Litengine \$110 for each engine. Litengine estimates a goodwill loss of \$500 for any order short.  

The demand pattern for the engine is exponential, with 

``` {r}
f<-function(x){(1/75)*exp(-1/75*x)}

cu<-1800-1000+500
co<-1000+180-110

lambda<-1/75

#encontrar el critical ratio
ratio<-cu/(cu+co)

#encontrar Qopt
qOpt<-qexp(p=ratio, rate=lambda)

```


