---
title: "Inventory RQ"
author: "adenadakuri"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

### Example1 (RQ)
The annual demand for sugar at a local soft drink manufacturer is normally distributed with $\lambda$=800 tons and $\sigma$=25 tons. The delivery times for sugar is 5 working days.  
We assume that there are 250 working days. 
```{r}
lambda11<-800#ton/year
sigma11<-25

leadTime11<- 5/250 #yr (tau)

#a)
demandTau11<-lambda11*leadTime11
sigmaTau11<-sigma11*sqrt(leadTime11)

safetyStock11<- 5#ton
Q11<-20 #ton

R11<-demandTau11+safetyStock11
  
#nivel de servicio 
serviceLevel11<-pnorm(R11, demandTau11, sigmaTau11, TRUE) #Lo multiplico por el formato.
serviceLevel11 

#Tasa de resurtido (Fill rate)
z11<-(R11-demandTau11)/sigmaTau11
lostFunctionNormal<-function(x){exp(-(x^2)/2)/sqrt(2*pi)-x*(1-pnorm(x))}
lostFunctionValue11<-lostFunctionNormal(z11)

fillRate11<-1-(lostFunctionValue11*sigmaTau11/Q11)
fillRate11

#b serviceLevel=95% ^ fillRate=95%

serviceLevel12<-0.95
safetyStock12<- qnorm(serviceLevel12)*sigmaTau11

fillRate12<-0.95
Lz12<-Q11*(1-fillRate12)/sigmaTau11

#USAR EL CODIGO DE LA TABLA DE MONCAYO
#z<-lossFunctionTable[rowZ,1]
#safetyStock3<-z*sigmaTau

```

El nivel de servicio que estamos dando es de `r serviceLevel11`


### Example 3
Textiles RU's, a textile sizing and dyeing plant uses a continuous review system (R,Q) to manage its dye inventory. The ordering cost is \$200, and a gallon of purple dye costs $5. Annual inventory holding cost is estimated at 20%. Expected annual demand is 10,000 gallons, and lead time demand is normally distributed with mean 400 and variance 900. 

1. Find the lead time $\tau$. 
``` {r}
K<-200
c<-5
i<-0.2
h<-i*c

lambda<-10000
lambdaTau<-400
sigmaTau<-30

#1)
tau<-lambdaTau/lambda

```

Res.  Tau= `r tau`

2. Find the reorder point for a service level of 90%, and the resulting safety stock.
``` {r}
alfa21<-0.9 #service level
R21<-qnorm(alfa21,lambdaTau, sigmaTau)
safetyStock21<-R21-lambdaTau

```
Res. El punto de reorden es de `r R21` galones.  El safety stock resultante es de `r safetyStock21`

3. Because of delivery convenience, the order quantity is set as 1000 gallons. If the estimated shortage cost per gallon is \$4, what is the reorder level that minimises the total expected cost? 
``` {r}
Q23<-1000
pi<-4

R22<-qnorm(1-((Q23*h)/(pi*lambda)), lambdaTau, sigmaTau)
safetyStock22<-R22-lambdaTau

```
Res. El punto de reorden resultante es de `r R22`, y el safety stock correspondiente es de `r safetyStock22`

### Example 3
Super-P is a peanut processing company. Past experience indicates that the annual
demand is normally distributed with $\lambda$ = 25’000 tons and a standard deviation of $\sigma$ =
36 tons. To order the peanuts, the company spends $50 to process the order. Each ton
of peanut costs $1’000, and the annual interest rate for evaluating inventory holding
cost is 25 percent. The penalty for a shortage is estimated to be $4 per ton. Ordering
lead time is approximately one week.  

Calculate the R* and Q*
``` {r}
#El problema es que si no conozco Q, no puedo encontrar el punto de reorden
qOpt<-function(lambda, K, pi,nR, h){sqrt(2*lambda*(K+pi*nR)/h)}
rOpt<-function(Q, h, pi, lambda, lambdaTau, sigmaTau){qnorm(1-((Q*h)/(pi*lambda)),lambdaTau, sigmaTau)}

lambda31<-25000 
tau31<-1*(1/52) #por que nos lo dan por semana.
lambdaTau31<-lambda31*tau31

sigma31<-36
sigmaTau31<-sigma31*sqrt(tau31)

K31<-50
pi31<-4
c31<-1000
i31<-0.25

h3<-i31*c31

#Para j=0
nR3<-0
Q30<-qOpt(lambda31,K31,pi31, nR3, h3)
R30<-rOpt(Q30,h3,pi31,lambda31,lambdaTau31, sigmaTau31)
nR30<-lostFunctionNormal(1-((Q30*h3)/(pi31*lambda31)))*sigmaTau31

```


